---
title: "Indagine sulle esigenze tecnico-scientifiche a supporto della ricerca"
output: html_notebook
---



```{r global, include=FALSE}
library(shiny)
library(shinydashboard)
library (DT)
library(tidyverse)
library(googlesheets)
library(topicmodels)
library(tidytext)
library(tm)
library(ggthemes)
library(wordcloud2)
library(wordcloud)
library(plyr)



dati<-gs_title("Integrazione tecnico-scientifica alle attività amministrative a supporto della ricerca (Risposte)")
ds <-gs_read(dati, ws="Risposte del modulo 1" )

names(ds)[c(5,6,7,8)]<-c("Estero", "Ruolo", "Risposta", "Servizio")

ds<- ds %>% drop_na(Risposta)
ds<-ds %>% 
  mutate(id=seq(1:dim(ds)[1]))
ds$Professione<-revalue(ds$Professione, c("Collaboratore tecnico professionale addetto ai servizi di laboratorio"="Tecnico di laboratorio", "Tecnico sanitario di laboratorio biomedico"="Tecnico di laboratorio"))
                         
ds$Ruolo<-revalue(
  ds$Ruolo, c(
    "Tecnico" ="Tecnico di laboratorio" , 
    "Collaboratore tecnico professionale addetto ai servizi di laboratorio"=
      "Tecnico di laboratorio" , "professional e gestionale" ="Gestionale e tecnico/scientifico" , "gestionale e professional"  ="Gestionale e tecnico/scientifico" , "gestionale con mantenimento di attività tecnico-scientifica"="Gestionale e tecnico/scientifico" ))
```

```{r for, echo=FALSE}

f<-ds %>% 
  group_by(Formazione) %>% 
  dplyr::summarise(Risposte=n(), "Età media"=mean(`Età`, na.rm=TRUE),"Anni di Servizio"=median(Servizio, na.rm=TRUE)) %>% 
  mutate_if(is.numeric, funs(round(.,digits = 2))) 
  
  datatable(f,rownames = FALSE,option=list(dom = 't',searching = FALSE,paging = TRUE,autoWidth = TRUE) )
```

```{r prof, echo=FALSE}
p<-ds %>% 
  group_by(Professione) %>% 
  dplyr::summarise(Risposte=n(), "Età media"=mean(`Età`, na.rm=TRUE),"Anni di Servizio"=median(Servizio, na.rm=TRUE)) %>% 
  mutate_if(is.numeric, funs(round(.,digits = 2))) 
  
  datatable(p,rownames = FALSE,option=list(dom = 't',searching = FALSE,paging = TRUE,autoWidth = TRUE) )
```

```{r ruolo echo=FALSE}
r<-ds %>% 
  group_by(Ruolo) %>% 
  dplyr::summarise(Risposte=n(), "Età media"=mean(`Età`, na.rm=TRUE),"Anni di Servizio"=median(Servizio, na.rm=TRUE)) %>% 
  mutate_if(is.numeric, funs(round(.,digits = 2))) 
  
  datatable(r,rownames = FALSE,option=list(dom = 't',searching = FALSE,paging = TRUE,autoWidth = TRUE) )




```







Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
